---
title: "Behavioural addictions research past & present: A bibliographic review"
author: "Rob Heirene$^1$"
date: "`r format(Sys.time(), '%d %B, %Y')`"
execute: # prevent code and execution messages showing
  echo: false
  warning: false
  message: false
format:
  pdf:
    toc: false # No contents table
    include-in-header:
      text: |
       \usepackage{setspace}
       \onehalfspacing
       \addtokomafont{disposition}{\rmfamily} 
        \setlength{\parindent}{2em}  
bibliography: references.bib
csl: cardiff-university-vancouver.csl
---

```{r output=FALSE, warning = FALSE, messages=FALSE}
# Install and load the groundhog package to ensure consistency of the package versions used here:
# install.packages("groundhog") # Install

# Load in packages using `groundhog` to ensure consistency of the versions used here:

library(groundhog) # Load
 
# set.groundhog.folder("C:/Users/rhei4496/Groundhog packages") # Set in a writable directory
get.groundhog.folder()

# List desired packages:
packages <- c("tidyverse", 
              'readr', # Load dataset from GitHib
              'RCurl', # Load dataset from GitHib
              'gtExtras', # Add colours to gt tables
              'transformr', # Needed for certain animations (dumbell lines)
              'png',# Helps render gganimate plots
              'gifski', # Helps render gganimate plots
              'rmarkdown', # Helps render gganimate plots
              'av', # render gganimate plots as videos
              'Cairo', # Anti-aliasing for the line plots (smoothing output)
              'ggtext', # make fancy labels in plots
              'sysfonts', # Special fonts for figures
              'showtext', # Special fonts for figures
              'scico', # Colour palette
              'kableExtra', # Make tabless
              'formattable', #  Add visualisations to tables
              'gt', # Alternative table options
              'gtsummary', # Create summary tables
              'scales', # Allows for the removal of scientific notation in axis labels
              'ggrain', # Make rain cloud plots
              'waffle', # make waffle plots for proportions
              'networkD3', # Make Sankey plots to show relationships
              'patchwork', # Join plots in multipanel layouts
              'pwr', # Check statistical power
              'car', # Perform ANCOVA stats tests
              'rstatix', # Perform ANCOVA stats tests
              'ggpubr', # Plots for linearity checks 
              'broom', # Print summaries of statistical test outputs
              'psych', # get detailed summary figures to Supplement statistical tests
              'ggstatsplot', # Plots with statistical outputs
              'janitor', # Make column names consistent format
              'caret', # Compute model performance indices
              'sessioninfo', # Detailed session info for reproducibility
              "osfr",
              "readxl",
              # "Gmisc", # Produce prisma flow diagram
              # 'grid', # Produce prisma flow diagram
              # "glue", # Produce prisma flow diagram
              "apa", # print test results in apa format
              "apaTables", # print test results in apa format
              "ggh4x", # truncate graph axis lines
              "truncnorm", # Generate normally distributed data with limits
              "ComplexUpset" # produce upset plots
)
# Load desired package with versions specific to project start date:
groundhog.library(packages, "2024-05-30")
                  # force.install=TRUE) 
                  # tolerate.R.version = '4.4.0')

# groundhog.library(packages, "2023-12-29") 

```

```{r message = FALSE, warning = FALSE}

## Setup presentation & graph specifications. Set up a standard theme for plots/data visualisations:

# Load new font for figures/graphs
font_add_google("Poppins")
font_add_google("Reem Kufi", "Reem Kufi")
font_add_google("Share Tech Mono", "techmono")
windowsFonts(`Segoe UI` = windowsFont('Segoe UI'))
showtext_auto()
showtext_auto(enable = TRUE)

# Save new theme for figures/graphs.This will determine the layout, presentation, font type and font size used in all data visualisations presented here:
plot_theme<- theme_classic() +
  theme(
    text=element_text(family="Poppins"),
    plot.title = element_text(hjust = 0.5, size = 16),
          plot.subtitle = element_text(hjust = 0.5, size = 13),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12),
    plot.caption = element_text(size = 12),
    legend.title=element_text(size=12), 
    legend.text=element_text(size=10)
        ) 
```

```{=tex}
\begin{center}

$^1$ School of Psychology, Brain \& Mind Centre, University of Sydney, Australia

\end{center}
```

------------------------------------------------------------------------

 

**Correspondence:** robert.heirene\@sydney.edu.au

**Conflicts of interest:** None

**Funding:** No funding was received for this project.

\newpage

# Abstract

------------------------------------------------------------------------

```{=tex}
\begin{center}

\textit{"... there is no basis for linking the word 'addiction' to drug habits. Nor is there a basis for assuming that the most severe addictions necessarily involve drugs."} 
 
B.K. Alexander \& R. F. Schweighofer (1988)
\end{center}
```
\newpage

# Introduction

The phrase "behavioural addiction" appears in academic articles in the early 1990s following ...'s seminal editorial. However, the notion that someone can be addicted to "activities" and not substances appears earlier (e.g., Alexander & Schweighofer, 1988), and parallels between compulsive gambling and substance addictions go back to at least ... ().

Immediately following ...'s editorial, Jaffe [1990; @Jaffe1990] made the argument that the term "addiction" was being used too liberally---it was being applied to many non-drug-related behaviours and there was a risk of "*trivializing dependence*". These concerns did little to stem the expanding definition of the term. Since Jaffe's 1990 article the net of addiction has been cast wider and wider, capturing increasingly more repetitive or compulsive behaviour patterns. These include... and even fortune telling [@Grall-Bronnec2015; @Skryabin2020].

Fears that the term addiction will lose its seriousness or weight remain heightened today [@Billieux2015]. These may be justified---individuals who experience addictions to opioid-based drugs or alcohol can suffer serious, life-threatening harm and withdrawal episodes. Assigning the same label to describe their experience and someone who has a largely inconsequential difficulty controlling their spending or screen use could indeed trivialise the condition. Yet, there is increasing evidence that people are compulsively engaging with behaviours like gambling (), gaming (), smart phones (), and exercise () in a way that resembles substance addictions. Neuroscientific studies have indicated that the neurobiology underlying substance and behavioural addictions may also be similar (see ...).

Buoyed by this evidence, clinicians and researchers have lobbied for increased recognition of behavioural addictions as official mental health diagnoses. Success in this endeavour was most notable in 2013 when the American Psychological Association included *Gambling Disorder* as a behavioural addiction in the fifth edition of the Diagnostic & Statistical Manual of mental disorders (DSM-5) under the rubric of . More recently in 2018,

While the addition of Gambling Disorder to the DSM-5 appears to have been widely accepted as a positive step forward, the addition of Gaming Disorder to the ICD-11 has been met with contention.

Such concerns are not unique to the addiction field. "Psychiatrization" and "concept creep" have been used to describe the seemingly ever-widening definitions mental health disorders, abuse, and trauma, as well as the "medicalisation" of these in the form of over-diagnosis and treatment (Haslam, 2016; Haslam et al., 2021).

Whilst others have expressed concern about this issue in the behvioural addictions field [e.g., @Billieux2015], there has been no attempt to systematically investigate this trend and "take stock" of research in the field. The number of novel addictions formally investigated remains unclear. As does the extent to which each purported addiction has been studied relative to the more established gambling and gaming disorders. The aim of this bibliographic review was, therefore, to determine:

\[1\] the total number of different behavioural addictions formally studied in peer-reviewed articles

\[2\] the number of such articles focused on each proposed addiction

# Methods

PRISMA\

A novel, exploratory approach was to identify relevant behavioural addictions and related articles. As such, pre-registration of the methods was not deemed appropriate or possible.

An important assumption that underlay the methods used here was that

## Search & selection process

The review was divided into two phases. The first aimed to identify all potential behavioural addictions that *may* have been formally studied in peer-reviewed articles. This was achieved via internet-based searches of terms such as "new behavioural addiction" and "novel behavioural addictions", as well as scans of academic blogs (e.g., <https://drmarkgriffiths.wordpress.com/>). Terms for these novel addictions were collated and combined with diagnostic terms for more established behavioural addictions. For example, *Gambling Disorder* from the DSMs-5 [@edition2013diagnostic], *Pathological Gambling* from DSM-IV, and *Gaming Disorder* from ICD-11 [@worldhealthorganization2018].

In Phase 2, the terms derived from Phase 1 were used in searches of the PubMed database. PubMed was selected for two reasons. First, it indexes more than 30,000 different journals/outlets, including most journals that publish behavioural addiction research (e.g., *Addiction*, *Journal of Behavioural Addictions*, *Additive Behaviours*). Second, search results and article data can be automatically downloaded using the `rentrez` R package, allowing for efficient extraction of data on a large scale—in this case, all articles ever published on behavioural addictions in the database.

Search strings for each behavioural addiction were first trialled and refined using the PubMed "Advanced search" function online. Once a string was finalised, all results returned using it were screened for relevance at title and abstract level. To be included in the review, an article was required to:

-   

The title and PMID (PubMed ID) of irrelevant articles were noted and later removed (see Data extraction section below).

## Data extraction

used `rentrez` to pull the results from searches.

individually screening the results for duplicates or irrelevant articles (e.g., errata).

## Data analysis

```{r results=FALSE, warning=FALSE, message=FALSE}
# Now I'll load in the dataset and do a little cleaning. Of note, I'm going to remove all publications from 2023 so that we only have data for complete years (see comments in the code chunk below for any other exclusions).

#| code-fold: true
#| code-summary: "Code: load dataset"

url_behav_addic_data_link <- "https://raw.githubusercontent.com/rheirene/pub-med-scape-behav-addictions/main/Data%20extraction/combined_results_clean.csv"

raw_data <- read_csv(url_behav_addic_data_link) %>%
  as_tibble()

str(raw_data)

# Despite my best efforts with manual searching, my explorations of this dataset in R revealed that there are a few erratums/corrigendums and one notice of retraction included in the data. Let's remove these before moving forward:
filtered_data <- raw_data %>%
  filter(str_detect(Publication_Type, "Erratum") | 
         str_detect(Publication_Type, "corrigendum") | 
         str_detect(Publication_Type, "Retraction")) %>% 
  distinct(PMID, .keep_all = TRUE)

# Let's now remove these pubs and any from 2023 so we have data for all "full" years:
data <- raw_data %>% 
  anti_join(filtered_data) %>%
    filter(Year != "2023") 

# View(data)

```

```{r include=FALSE}
data %>%
  distinct(PMID) %>%
  nrow() %>%
  as_tibble() %>%
  mutate(full_count = nrow(data)) %>%
  mutate(full_unique_discrepancy = full_count-value) %>%
  rename(unique_count = value)

# Get palette colors
num_labels <- length(unique(data$Label))
palette_colors <- rev(scico(n = num_labels, palette = 'imola'))


# data %>%
#   distinct(PMID, .keep_all = TRUE) %>%
#   group_by(Label) %>% 
#   filter(Year %in% c(min(Year), max(Year)))

# Find the first and last study for each "addiction" with number of papers at these years:
data %>%
  distinct(PMID, .keep_all = TRUE) %>%
  group_by(Label) %>% 
  summarise(
    min = min(Year), # identify first year
    max = max(Year) # identify last  year
  ) %>% 
  arrange(min) 
```

### 

```{r warning=FALSE, message=FALSE}
#| code-fold: true
#| code-summary: "Code: Table all addictions"

# Arrange data:
data %>%
  group_by(Label) %>% 
  summarise(
    n = n()
  ) %>%
  mutate(percent = round(n/sum(n)*100,2)) %>%
  arrange(desc(n)) %>%
      # Tidy the behavioural addiction labels:
    mutate(Label = str_replace_all(Label, "_", " ") %>%
                 str_to_title()) %>%
   gt() %>% # Turn dataframe into gt table
   tab_header(
    title = md("**Number of behavioural addiction articles on PubMed**"),
    subtitle = md("*Up to end of 2022*"))  %>%
  tab_options(data_row.padding = px(1.6)) %>% # decrease row height
    tab_style(
    style = cell_borders(sides = c("t", "b"),
                         weight = px(2)),
    locations = list(cells_column_labels(), cells_stubhead())
  ) %>%
   cols_align(align = "center", columns = c(n, percent)) %>%
   cols_align(align = "right", columns = Label) %>%
  tab_style(
    style = cell_borders(sides = c("t"),
                         weight = px(2)),
    locations = list(cells_footnotes(), cells_source_notes())
  ) %>%
       cols_label(
    Label = "Behavioural addiction",
    n = "N",
    percent = "%") 
  

```

# Results

```{r  warning=FALSE, message=FALSE, results= FALSE}
#| code-fold: true
#| code-summary: "Code: Bar chart of total pubs"
#| fig-align: center


# Compute some summary values will use in the labels:
n_papers_2022<- data %>%
  distinct(PMID, .keep_all = TRUE) %>%
  filter(Year == 2022) %>%
  distinct(PMID) %>% 
  count() %>%
  pull()

n_journals_2022<- data %>%
  distinct(PMID, .keep_all = TRUE) %>%
  filter(Year == 2022) %>%
  distinct(Journal_Title) %>% 
  count() %>%
  pull()

# Prepare data:
data_total_per_year_pubs <- data %>%
   distinct(PMID, .keep_all = TRUE) %>%
   filter(Year != "2023") %>%
   group_by(Year) %>%
   count() %>%
   ungroup()
 
                   
 # Make plot: 
hist_yearly_total<- data_total_per_year_pubs %>%
  ggplot(aes(x = as.integer(Year), y = n)) + 
  geom_bar(stat = "identity", fill = "#00798c", color = "black", width = 0.9) +
  labs(y = "", x = "") +
  # labs(y = "No. of publications", x = "") +
  scale_x_continuous(breaks = seq(1960, 2020, by = 20)) +
  scale_y_continuous(breaks = seq(0, 1200, by = 400)) +
  plot_theme 
  # theme(plot.margin = unit(c(0, 0, 0, -2), 'cm'))

```

```{r warning=FALSE,  message=FALSE, results= FALSE}

# Arrange data:
dumbbell_plot_data<- data %>%
  # filter(Year != "2023") %>%
  filter(Label != "behavioural_addictions") %>%
  group_by(Label) %>% 
  summarise(
    min = min(Year), # identify first year
    max = max(Year), # identify last  year
    min_papers = sum(Year == min(Year)),  # Count papers for first year
    max_papers = sum(Year == max(Year))   # Count papers for last year
  ) %>% 
  arrange(min) %>% 
  pivot_longer(cols = c(min, max),
    names_to = "Range",
    values_to = "Year"
  ) %>%
  # Compute a single column that contains our n papers for the first and last pub years:
  mutate(papers_this_year = case_when(Range == "max" ~ max_papers, 
                                      Range == "min" ~ min_papers)) %>%
  select(-min_papers,
         -max_papers) %>% 
  # Add a value that tells us whether a date is min or max for colouring later:
    # Tidy the behavioural addiction labels:
    mutate(Label = str_replace_all(Label, "_", " ") %>%
                 str_to_title())

# Order the behavioural addictions based on the first year of publication
label_order <- dumbbell_plot_data %>% 
  filter(Range == "min") %>% 
  arrange(Year) %>% 
  pull(Label)

# Fix the order:
dumbbell_plot_data$Label <- factor(dumbbell_plot_data$Label, levels = rev(label_order))

# Create data for every publication year per label
every_year_data <- data %>%
  filter(Label != "behavioural_addictions") %>%
  group_by(Label, Year) %>%
  summarise(n_papers = n()) %>%
  ungroup() %>%
  mutate(Label = str_replace_all(Label, "_", " ") %>%
                 str_to_title())

  # Plot: 
dumbbell_plot_first_last <- ggplot() +
  geom_line(data = dumbbell_plot_data, aes(x= Year, y= Label),
            size = 1,
            colour="#666666") +
  geom_point(data = every_year_data, aes(x = Year, y = Label, size=n_papers), color="black", alpha=0.2) +
  geom_point(data = dumbbell_plot_data, aes(x = Year, y = Label, color=Range, size=papers_this_year)) +
  # scale_size_continuous(guide="none") +
  scale_color_manual(values = c("min" = "#00798c", "max" = "#00798c"), guide= "none") +
  plot_theme +
  labs(y = "", x = "Year") +
  theme(
        legend.position = c(0.3, 0.14),  # Position the legend in the bottom left corner
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        legend.background = element_rect(color = "black", size = 1))+ # Add border around the legend) +
  guides(size = guide_legend(title = "No. papers", override.aes = list(color = "#00798c"))) 

 # labs(
  #  title = sprintf("<span style = 'color: #70A377;'>Earliest</span> and <span style = 'color: #50B5C8;'>most recent</span> studies of behavioural addictions on PubMed"))

 # View static plot
```

```{r}
#| fig-align: center
#| fig-width: 5
#| fig-height: 7
# Join plots together and present them:

hist_yearly_total / dumbbell_plot_first_last +
  plot_layout(heights = c(3.5, 14)) +
  plot_annotation(tag_levels = 'A') &
  theme(plot.tag.position = c(0.03, 1))
```

```{r}
#| fig-align: center
#| fig-width: 8
#| fig-height: 5
# Prepare the data for UpSet plot
upset_data <- data %>%
  select(Title, Label) %>%
  mutate(Label = str_replace_all(Label, "_", " "),
         Label = str_to_title(Label)) %>%
  group_by(Title, Label) %>%
  summarize(Presence = TRUE, .groups = 'drop') %>%
  pivot_wider(names_from = Label, values_from = Presence, values_fill = list(Presence = FALSE))

# Extract the unique labels for UpSet plot
behav_addiction <- data$Label %>%
  unique() %>%
  str_replace_all("_", " ") %>%
  str_to_title()

# Generate the UpSet plot
upset(
  upset_data,
  intersect = behav_addiction,
  name = '',
  # width_ratio = 0.1,
  height_ratio = 1,
  min_size=10, 
  set_size = FALSE,
  # keep_empty_groups=TRUE,
  # wrap=TRUE,
  themes=upset_modify_themes(
  list(
    'intersections_matrix' = theme(
      text = element_text(family = "poppins", size = 12),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      panel.border = element_blank()
    ),
    'overall_sizes' = theme(
      text = element_text(family = "poppins", size = 12),
      axis.text.x = element_text(angle = 90),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      panel.border = element_blank()))),
  base_annotations = list(
        'No. papers per intersection'=intersection_size(
            # counts=FALSE,
           text=list(
                      # vjust=-0.4,
                      # hjust=.2,
                      angle=0,
                      family = "Poppins",
                      size = 2.1
                    ),
           mapping=aes(fill='bars_color')
        ) + scale_fill_manual(values=c('bars_color'='#00798c'), guide='none')) 
)


```

# Discussion

```{=tex}
\begin{center}

\textit{"I found myself saying to our driver: 'Green, did you know that I am an addict'? He is of the old school so that he did not turn his head. 'No, sir, I did not know that'. 'I am addicted to at least one good experment a day---sometimes I can arrange it by telephone. When I cannot, the world goes out of focus, becomes unreal'. Possibly somewhat dissapointed, but cearly relieved: `I see, sir`."}

E. H. Land in \textit{Addiction as Necessity and Opportunity} (1971).
\end{center}
```
# References

-   Alexander, B. K., & Schweighofer, A. R. F. (1988). Behavioural Addictions. *Canadian Journal of Psychology*, 29, 151-163.

-   Haslam, N. (2016). Concept creep: Psychology's expanding concepts of harm and pathology. *Psychological Inquiry, 27*(1), 1--17. [https://doi.org/10.1080/1047840X.2016.1082418](https://psycnet.apa.org/doi/10.1080/1047840X.2016.1082418)

```{r}
#| code-fold: true
#| code-summary: "Code: Get session info"

# session_info(pkgs = "attached")
```
